---
title: "First 10 Graphs"
author: "Ben Goldstone"
date: "9/6/2023"
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)    # Load additional packages here 
require(ggformula) # formula interface to ggplot2
require(readr)
require(AER)
# Some customization.  You can alter or delete as desired (if you know what you are doing).

theme_set(theme_bw()) # change theme for ggplot2
trellis.par.set(theme=theme.mosaic()) # change default color scheme for lattice

knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```

## College Distance Data Import
[College Distance Dataset](https://vincentarelbundock.github.io/Rdatasets/doc/AER/CollegeDistance.html)
```{r}
collegeDistance <- read_csv("~/CSVs/CollegeDistance.csv")
head(collegeDistance)
```

### Urban College
```{r}
gf_bar(~urban,data=collegeDistance,fill=~urban)
```

### Composite test scores and gender
```{r}
gf_boxplot(score~gender,data=collegeDistance, fill=~gender)

```

### Home owner and income level
```{r}
gf_bar(~income|home,data=collegeDistance, fill=~income)
```

### Region and distance divided by income level   
```{r}
gf_boxplot(distance~income|region,data=collegeDistance, fill=~income)
```

## China Income Data Import
[China Income Dataset](https://vincentarelbundock.github.io/Rdatasets/doc/AER/ChinaIncome.html)
```{r}
ChinaIncome <- read_csv("~/CSVs/ChinaIncome.csv")
head(ChinaIncome)
```

### Construction Income over Time
```{r}
gf_point(constructionIncome~year,data=ChinaIncome,color = ~ (constructionIncome > 1000))
```

### Construction Income
```{r}
gf_density(~constructionIncome,data=ChinaIncome)
```

### Industry Income and Agriculture Income
```{r}
gf_hex(industryIncome~agricultureIncome, data=ChinaIncome) %>% gf_lm() %>% gf_refine(scale_fill_viridis_c())

industry = "blue"
agriculture="darkgreen"
gf_line(industryIncome~year,data=ChinaIncome,color=industry) %>% gf_line(agricultureIncome~year,data=ChinaIncome,color=agriculture) %>% gf_text(x=1988,y=4750,label="industry",color=industry,hjust = 1.2) %>% gf_text(x=1988,y=500,color=agriculture,label="agriculture", hjust=1.2)
```

## Consumer Goods Data Import
[Consumer Goods Dataset](https://vincentarelbundock.github.io/Rdatasets/doc/AER/ConsumerGood.html)
```{r}
ConsumerGood <- read_csv("~/CSVs/ConsumerGood.csv")
head(ConsumerGood)
```

### Share and distribution of consumer goods
```{r}
gf_point(share~distribution, data=ConsumerGood) %>% gf_lm()
```

### Price of Consumer Goods over time
```{r}
gf_point(price~rownames,data=ConsumerGood) %>% gf_lm()
```

### Price and distribution of Consumer Goods
```{r}
gf_point(price~distribution,data=ConsumerGood) %>% gf_lm()
```