---
title: "Project 4 Data Collection"
author: "Ben Goldstone"
date: "4/21/2023"
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```


# Data Set
```{r}
library(readr)
datascience_salaries <- read_csv("~/CSVs/ds_salaries.csv")
head(datascience_salaries)

```
# Columns
Data Science Job Salaries Dataset contains 11 columns, each are:

**work_year:** The year the salary was paid.

**experience_level:** The experience level in the job during the year. (SE:Senior,
EN:Entry level, EX:Executive level, MI:Mid/Intermediate level)

**employment_type:** The type of employment for the role.
<!-- CT: Consulting? -->

**job_title:** The role worked in during the year.

**salary:** The total gross salary amount paid.

**salary_currency:** The currency of the salary.

**salaryinusd:** The salary in USD.

**employee_residence:** Employee's primary country of residence in during the work year as an ISO 3166 country code.

**remote_ratio:** The overall amount of work done remotely.

**company_location:** The country of the employer's main office or contracting branch.

**company_size:** The median number of people that worked for the company during the year.

# Data Source
This data was sourced from [AI-jobs.net](https://ai-jobs.net/). AI-Jobs.net seems to connect directly to employers for posting information on jobs. This [dataset](https://www.kaggle.com/datasets/ppb00x/credit-risk-customers) is from Kaggle datasets.

The data does not seem to have a direct source for it's data besides specifying that they "Provide a direct link between candidates and employers."
