---
title: "Chi-Square Practice"
author: "Ben Goldstone"
date: "4/21/23"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  pdf_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```


```{r}
library(readr)
Spring2023Dataset <- read_csv("~/CSVs/Spring2023Dataset.csv")
head(Spring2023Dataset)
```

```{r}
gf_bar(~GiveUp|CoffeeFreq,data=na.omit(Spring2023Dataset))
tal = tally(~GiveUp|CoffeeFreq,data=na.omit(Spring2023Dataset))
tal
```
# Trends
Of the people who hardly ever drink a lot of Coffee, chose to give up Caffeine. On the opposite extreme, of the people who drink Coffee almost daily, few choose to give up caffeine.

```{r}
xchisq.test(tal)
```
# Problems
Not all expected counts meet the minimum threshold of 5.

# Calculations
df = (4-1)*(4-1)=9


largest difference is between those who drink coffee almost daily and chose to give up caffeine, which means, in this case, we expected less people to give up coffee than our observed.


The Chi-Squared is calculated by adding all of the partial chi-squared (contributions) together.



