---
title: "Regression Computer Lab"
author: "Ben Goldstone"
date: "2/10/23"
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```


# Import Data

```{r}
library(readr)
Spring2023Dataset <- read_csv("~/CSVs/Spring2023Dataset.csv")
head(Spring2023Dataset)
```
# Texts Sent and Texts Received 
```{r}
gf_point(TextsReceived~TextsSent,data=Spring2023Dataset,alpha=0.3) %>%
  gf_lm()

```

# Observation
The relationship between texts received and texts sent seem to fit the line with a positive strong correlation.


# R Calculations
```{r}
# r
cor(TextsReceived~TextsSent,data=na.omit(Spring2023Dataset))
# r^2 as a percentage
(cor(TextsReceived~TextsSent,data=na.omit(Spring2023Dataset))^2)*100


```

Text sent accounted for 83% of the variability in the amount of texts sent.

# Linear Model
```{r}
  model=lm(TextsReceived~TextsSent,data=na.omit(Spring2023Dataset))
  summary(model)
```

# Linear Model Context
For every additional 1 text sent, we can expect an additional 1.07 text received. For 0 texts sent, we can expect 3.89 texts received.

```{r}
slope = 1.07061
intercept = 3.88943
response = 300*slope + intercept

response
```

# Prediction
Since sending 300 texts is outside of the range of 0 to 220, we cannot be confident in the result we receive.

# Residual Analysis
For the one person who sent 100 texts and received 250 texts, the residual would be high compared to the majority of the other points since it is about 125 texts above the linear regression line. Since the residual is above the line, it should be positive.