---
title: "Two Sample Means Computer Lab"
author: "Ben Goldstone"
date: "3/31/23"
output: 
  pdf_document:
    fig_height: 3
    fig_width: 5
  html_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```



```{r}
library(readr)
Spring2023Dataset <- read_csv("~/CSVs/Spring2023Dataset.csv")
head(Spring2023Dataset)
gf_boxplot(TextsSent~Personality,data=na.omit(Spring2023Dataset), fill=~Personality)
```


According to the boxplot expressing the relationship between **personalities** and **texts sent**, people who are extroverted on average send more texts than those that are introverted.


```{r}

favstats(TextsSent~Personality,data=na.omit(Spring2023Dataset))

```


On average people who are extroverted send 30.2 more texts than those who are introverted.


```{r}

t.test(TextsSent~Personality, data=Spring2023Dataset, conf.level=0.9)

```

I am 90% confident that the difference between texts sent based on personality is between 11 and 49.


We can conclude that on average extroverts send more texts given that 0 is not in the 90% confidence interval.

