---
title: "Project 3 Data Collection"
author: "Benjamin Goldstone & Anthony Panuccio"
date: "March 24, 2023"
output: 
  html_document:
    fig_height: 3
    fig_width: 5
  pdf_document:
    fig_height: 3
    fig_width: 5
  word_document:
    fig_height: 3
    fig_width: 5
---

```{r, setup, include=FALSE}
require(mosaic)   # Load additional packages here 
knitr::opts_chunk$set(
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
```
# Collection Method and Description
Using a ball and a bucket both of us did 20 trials with different hands and angles based on a random number from a random number generator to see if there is evidence that one way of throwing a ball is dominant. Each hand/angle combination was assigned a number from 1-4.

1. Left Over
2. Right Over
3. Left Under
4. Right Under

# Variables

Response: Make or Miss
Explanatory: Overhand/Underhand and Right Hand/Left Hand

```{r}
library(readr)
DataCollectionProject3 <- read_csv("DataCollectionProject3.csv")
head(DataCollectionProject3)
```

